|

### 2021-03-08 supplementary_information_science.Rmd
edits: equations

$$
\mu_{z,k} = \rho \mu_{z,k+1} + \epsilon_{k}
$$

@@

$$
\begin{aligned}
\mu_{z,k} &= \omega(\rho \mu_{z,k+1}^R + \epsilon_{k}^R) + (1-\omega)(\rho \mu_{z,k+1}^L + \epsilon_{k}^L) \\
\omega &= \frac{A_{k+1}^R}{A_{k+1}^R + A_{k+1}^L}
\end{aligned}
$$

@@

$$
N_{ix}(t + 1) \sim Poisson(n_{ix}(t) + I_{ix}(t) - E_{ix}(t))
$$

@@

$$
n_{ix}(t) = \frac{N_{ix}(t)r_{ix}(t)}{1 + \frac{r_{0,i}-1}{K_{x}}\sum_{j=1}^S{\alpha_{ij}N_{jx}(t)}}
$$

@@

$$
r_{ix}(t) = \delta~r_{0,i}~exp[{-\frac{\{\mu_i-z_x(t)\}^2}{2\sigma^2_{niche,i}}}]
$$

@@

$$
\delta = exp(-\frac{\sigma_{niche,i}^2}{2\nu^2})
$$

@@

$$
\Omega_{xy} = \sigma_z^2~exp(-\phi d_{xy})
$$

@@

$$
\xi_{ix}(t) = \frac{\sum_{y,y \neq x}E_{iy}(t)~exp(-\theta d_{xy})}{\sum_{x} \sum_{y,y \neq x}E_{iy}(t)~exp(-\theta d_{xy})}
$$

@@

$$
\mu_w = \xi_0 + \xi_1~log_{10}~WA_w + \xi_2~log_{10}~P_{b,w} + \xi_3~region_w + \sum_k \xi_k x_{k,w}
$$

@@

$$
\begin{aligned}
\mu_w =& \xi_0 + \xi_1~log_{10}~WA_w + \xi_2~log_{10}~P_{b,w} + \xi_3~region_w +\\
&\xi_4~log_{10}~WA_w \cdot region_w + \xi_5~log_{10}~P_{b,w} \cdot region_w + \sum_k \xi_k x_{k,w}
\end{aligned}
$$

@@

$$
Bayes~factor = exp(\Delta BIC_{10}/2)
$$

@@

$$
\begin{aligned}
log_{10}~y_j &\sim Normal(\mu_j, \sigma^2)\\
       \mu_j &= \psi_0 + \psi_1~log_{10}~N_{p,j} + \psi_2~log_{10}~P_{b,j}
\end{aligned}
$$

@@

$$
\begin{aligned}
u_{n} &\sim Normal(\mu_n, \sigma^2)\\
\mu_n &= \zeta_0 + \zeta_1 \sigma_{h,n} + \zeta_2 \sigma_{l,n} + \zeta_3 \sigma_{z,n} + \zeta_4 \phi_n + \zeta_5 \nu_n + \zeta_6 \alpha_{max, n} + \zeta_7 \theta_n + \zeta_8 p_{d,n} 
\end{aligned}
$$

@@

$$
\%~bias = \frac{100(S_{est} - S_{true})}{S_{true}}
$$

@@

$$
\delta_u(u^{(1)} \to u^{(2)}, v, \Theta) = \frac{E(y|u^{(2)}, v, \Theta) - E(y|u^{(1)}, v, \Theta)}{u^{(2)} - u^{(1)}}
$$

@@

$$
\Delta_u = \frac{\int\int_{u^{(2)}>u^{(1)}}du^{(1)}du^{(2)}\int dv \int d\Theta (E(y|u^{(2)}, v, \Theta) - E(y|u^{(1)}, v, \Theta))~p(u^{u^{(1)}}|v)~p(u^{u^{(2)}}|v)~p(v)~p(\Theta)}{ \int\int_{u^{(2)}>u^{(1)}}du^{(1)}du^{(2)}\int dv \int d\Theta~(u^{(2)} - u^{(1)})~ p(u^{u^{(1)}}|v)~p(u^{u^{(2)}}|v)~p(v)~p(\Theta) }
$$

@@

$$
\hat\Delta_u = \frac{\sum_{i=1}^n \sum_{j=1}^n \sum_{s=1}^S w_{ij}(E(y|u_j, v_i, \Theta_s) - E(y|u_i, v_i, \Theta_s))sign(u_j - u_i)}{\sum_{i=1}^n \sum_{j=1}^n \sum_{s=1}^S w_{ij}(u_j - u_i)sign(u_j - u_i)}
$$

@@

$$
w_{ij} = w(v_i, v_j)
$$

@@

$$
w(v_i, v_j) = \frac{1}{1 + (v_i - v_j)^T\sum_v^{-1}(v_i-v_j)}
$$

@@

$$
\hat \Delta_{u,s} = \frac{\sum_{i=1}^n \sum_{j=1}^n w_{ij}(E(y|u_j, v_i, \Theta_s) - E(y|u_i, v_i, \Theta_s))sign(u_j - u_i)}{\sum_{i=1}^n \sum_{j=1}^n w_{ij}(u_j - u_i)sign(u_j - u_i)}
$$

@@

$$
S.E.(\hat \Delta_{u,s}) = \sqrt{\frac{1}{S-1} \sum_{s-1}^S (\hat \Delta_{u,s} - \hat \Delta_{u})^2}
$$

>>>>

\begin{equation}
  \mu_{z,k} = \rho \mu_{z,k+1} + \epsilon_{k}
\end{equation}

@@

\begin{equation}
\begin{aligned}
  \mu_{z,k} &= \omega(\rho \mu_{z,k+1}^R + \epsilon_{k}^R) + (1-\omega)(\rho \mu_{z,k+1}^L + \epsilon_{k}^L) \\
  \omega &= \frac{A_{k+1}^R}{A_{k+1}^R + A_{k+1}^L}
\end{aligned}
\end{equation}

@@

\begin{equation}
  N_{ix}(t + 1) \sim Poisson(n_{ix}(t) + I_{ix}(t) - E_{ix}(t))
\end{equation}

@@

\begin{equation}
  n_{ix}(t) = \frac{N_{ix}(t)r_{ix}(t)}{1 + \frac{r_{0,i}-1}{K_{x}}\sum_{j=1}^S{\alpha_{ij}N_{jx}(t)}}
\end{equation}

@@

\begin{equation}
  r_{ix}(t) = \delta~r_{0,i}~exp[{-\frac{\{\mu_i-z_x(t)\}^2}{2\sigma^2_{niche,i}}}]
\end{equation}

@@

\begin{equation}
  \delta = exp(-\frac{\sigma_{niche,i}^2}{2\nu^2})
\end{equation}

@@

\begin{equation}
  \Omega_{xy} = \sigma_z^2~exp(-\phi d_{xy})
\end{equation}

@@

\begin{equation}
  \xi_{ix}(t) = \frac{\sum_{y,y \neq x}E_{iy}(t)~exp(-\theta d_{xy})}{\sum_{x} \sum_{y,y \neq x}E_{iy}(t)~exp(-\theta d_{xy})}
\end{equation}

@@

\begin{equation}
  \mu_w = \xi_0 + \xi_1~log_{10}~WA_w + \xi_2~log_{10}~P_{b,w} + \xi_3~region_w + \sum_k \xi_k x_{k,w}
\end{equation}

@@

\begin{equation}
\begin{aligned}
  \mu_w =& \xi_0 + \xi_1~log_{10}~WA_w + \xi_2~log_{10}~P_{b,w} + \xi_3~region_w +\\
  &\xi_4~log_{10}~WA_w \cdot region_w + \xi_5~log_{10}~P_{b,w} \cdot region_w + \sum_k \xi_k x_{k,w}
\end{aligned}
\end{equation}

@@

\begin{equation}
  Bayes~factor = exp(\Delta BIC_{10}/2)
\end{equation}

@@

\begin{equation}
\begin{aligned}
  log_{10}~y_j &\sim Normal(\mu_j, \sigma^2)\\
         \mu_j &= \psi_0 + \psi_1~log_{10}~N_{p,j} + \psi_2~log_{10}~P_{b,j}
\end{aligned}
\end{equation}

@@

\begin{equation}
\begin{aligned}
  u_{n} &\sim Normal(\mu_n, \sigma^2)\\
  \mu_n &= \zeta_0 + \zeta_1 \sigma_{h,n} + \zeta_2 \sigma_{l,n} + \zeta_3 \sigma_{z,n} + \zeta_4 \phi_n + \zeta_5 \nu_n + \zeta_6 \alpha_{max, n} + \zeta_7 \theta_n + \zeta_8 p_{d,n} 
\end{aligned}
\end{equation}

@@

\begin{equation}
  \%~bias = \frac{100(S_{est} - S_{true})}{S_{true}}
\end{equation}

@@

\begin{equation}
  \delta_u(u^{(1)} \to u^{(2)}, v, \Theta) = \frac{E(y|u^{(2)}, v, \Theta) - E(y|u^{(1)}, v, \Theta)}{u^{(2)} - u^{(1)}}
\end{equation}

@@

\begin{equation}
  \Delta_u = \frac{\int\int_{u^{(2)}>u^{(1)}}du^{(1)}du^{(2)}\int dv \int d\Theta (E(y|u^{(2)}, v, \Theta) - E(y|u^{(1)}, v, \Theta))~p(u^{u^{(1)}}|v)~p(u^{u^{(2)}}|v)~p(v)~p(\Theta)}
                  { \int\int_{u^{(2)}>u^{(1)}}du^{(1)}du^{(2)}\int dv \int d\Theta~(u^{(2)} - u^{(1)})~ p(u^{u^{(1)}}|v)~p(u^{u^{(2)}}|v)~p(v)~p(\Theta) }
\end{equation}

@@

\begin{equation}
  \hat\Delta_u = \frac{\sum_{i=1}^n \sum_{j=1}^n \sum_{s=1}^S w_{ij}(E(y|u_j, v_i, \Theta_s) - E(y|u_i, v_i, \Theta_s))sign(u_j - u_i)}
                      {\sum_{i=1}^n \sum_{j=1}^n \sum_{s=1}^S w_{ij}(u_j - u_i)sign(u_j - u_i)}
\end{equation}

@@

\begin{equation}
  w_{ij} = w(v_i, v_j)
\end{equation}

@@

\begin{equation}
w(v_i, v_j) = \frac{1}{1 + (v_i - v_j)^T\sum_v^{-1}(v_i-v_j)}
\end{equation}

@@

\begin{equation}
  \hat \Delta_{u,s} = \frac{\sum_{i=1}^n \sum_{j=1}^n w_{ij}(E(y|u_j, v_i, \Theta_s) - E(y|u_i, v_i, \Theta_s))sign(u_j - u_i)}
                           {\sum_{i=1}^n \sum_{j=1}^n w_{ij}(u_j - u_i)sign(u_j - u_i)}
\end{equation}

@@

\begin{equation}
  S.E.(\hat \Delta_{u,s}) = \sqrt{\frac{1}{S-1} \sum_{s-1}^S (\hat \Delta_{u,s} - \hat \Delta_{u})^2}
\end{equation}
